Posterior summarisation in Bayesian phylogenetics using Tracer 1.7

### 2017-12-15 manuscript/tracer17.tex
remove white-spaces

\author[Rambaut \textit{et~al.}]{ Andrew Rambaut\,$^{1}$, Guy Baele$^{2}$,  Dong Xie\,$^{3,4}$, Marc A.~Suchard\,$^{5,6,7}$, Alexei J.~Drummond\,$^{3,4}$}

@@

%\section*{Old Text}
%
%%You can also select the "Demographic Analysis" from the Analysis menu - This plots the distribution of demographic population sizes over time for a number of models (constant size, exponential growth \& logistic growth) that are available in BEAST. This involves you selecting the traces for each parameter of the model. You should only select the model that was actually run under BEAST (e.g., if you ran an exponential growth model, you shouldn't plot the constant population size model).
%
%%The "Analysis" menu also contains options for performing Bayesian Skyline reconstructions and for calculating Bayes Factors between runs.
%
%Feature list:
%\begin{itemize}
%\item KDEs
%\item cheap marginal likelihood estimators
%\item demographic trajectory reconstruction
%\end{itemize}
%
%%Model selection HME and AICM have been removed
%New features:
%\begin{itemize}
%\item Three trace types: real, integer, string
%\item Kernel density estimates
%\item Conditional posterior distribution
%%\item HME
%%\item AICM
%\end{itemize}
%
%%\begin{figure}[H]
%%\includegraphics[width=.5\textwidth]{./figures/comp-95HPD.pdf}
%%\caption{The comparison of  95\% HPD intervals from multi-trace}
%%\label{fig:comp95HPD}
%%\end{figure}
%
%%\begin{figure}[H]
%%\includegraphics[width=.5\textwidth]{./figures/jointPrInt.png}
%%\caption{The Joint probability table of two integer traces}
%%\label{fig:int:jointpr}
%%\end{figure}
%
%%\begin{figure}[ht]
%%\includegraphics[width=.5\textwidth]{./figures/frequency.pdf}
%%\caption{A frequency distribution for a continuous trace}
%%\label{fig:freq}
%%\end{figure}
%%\begin{figure}[ht]
%%\includegraphics[width=.5\textwidth]{./figures/multiKDE.pdf}
%%\caption{KDE of multiple traces}
%%\label{fig:multiKDE}
%%\end{figure}
%%\begin{figure}[ht]
%%\includegraphics[width=.5\textwidth]{./figures/joint-marginal.pdf}
%%\caption{The joint-marginal distribution of two selected traces}
%%\label{fig:trace}
%%\end{figure}
%%\begin{figure}[ht]
%%\includegraphics[width=.5\textwidth]{./figures/trace.pdf}
%%\caption{The selected traces against state}
%%\label{fig:trace}
%%\end{figure}
%
%
%\subsubsection*{Diagnostics:} Blah blah
%
%\subsubsection*{Demographic reconstruction:}
%
%%\subsubsection*{Model selection:}
%
%\subsubsection*{Conditional posterior distribution:}

>>>>

\author[Rambaut \textit{et~al.}]{
Andrew Rambaut\,$^{1}$,
Guy Baele$^{2}$,
Dong Xie\,$^{3,4}$,
Alexei J.~Drummond\,$^{3,4}$,
Marc A.~Suchard\,$^{5,6,7}$
}

@@

%\section*{Old Text}
%
%%You can also select the "Demographic Analysis" from the Analysis menu - This plots the distribution of demographic population sizes over time for a number of models (constant size, exponential growth \& logistic growth) that are available in BEAST. This involves you selecting the traces for each parameter of the model. You should only select the model that was actually run under BEAST (e.g., if you ran an exponential growth model, you shouldn't plot the constant population size model).
%
%%The "Analysis" menu also contains options for performing Bayesian Skyline reconstructions and for calculating Bayes Factors between runs.
%
%Feature list:
%\begin{itemize}
%\item KDEs
%\item cheap marginal likelihood estimators
%\item demographic trajectory reconstruction
%\end{itemize}
%
%%Model selection HME and AICM have been removed
%New features:
%\begin{itemize}
%\item Three trace types: real, integer, string
%\item Kernel density estimates
%\item Conditional posterior distribution
%%\item HME
%%\item AICM
%\end{itemize}
%
%%\begin{figure}[H]
%%\includegraphics[width=.5\textwidth]{./figures/comp-95HPD.pdf}
%%\caption{The comparison of  95\% HPD intervals from multi-trace}
%%\label{fig:comp95HPD}
%%\end{figure}
%
%%\begin{figure}[H]
%%\includegraphics[width=.5\textwidth]{./figures/jointPrInt.png}
%%\caption{The Joint probability table of two integer traces}
%%\label{fig:int:jointpr}
%%\end{figure}
%
%%\begin{figure}[ht]
%%\includegraphics[width=.5\textwidth]{./figures/frequency.pdf}
%%\caption{A frequency distribution for a continuous trace}
%%\label{fig:freq}
%%\end{figure}
%%\begin{figure}[ht]
%%\includegraphics[width=.5\textwidth]{./figures/multiKDE.pdf}
%%\caption{KDE of multiple traces}
%%\label{fig:multiKDE}
%%\end{figure}
%%\begin{figure}[ht]
%%\includegraphics[width=.5\textwidth]{./figures/joint-marginal.pdf}
%%\caption{The joint-marginal distribution of two selected tes}
%%\label{fig:trace}
%%\end{figure}
%%\begin{figure}[ht]
%%\includegraphics[width=.5\textwidth]{./figures/trace.pdf}
%%\caption{The selected traces against state}
%%\label{fig:trace}
%%\end{figure}
%
%
%\subsubsection*{Diagnostics:} Blah blah
%
%\subsubsection*{Demographic reconstruction:}
%
%%\subsubsection*{Model selection:}
%
%\subsubsection*{Conditional posterior distribution:}
